The Unicode Cookbook \linebreak for Linguists

### 2018-03-11 book/chapters/pitfalls.tex
resolves issue #28

Second, a single character may be rendered as a sequence of multiple glyphs. For
example, in Tamil one Unicode character may result in a combination of a
consonant and vowel, which are rendered as two adjacent glyphs by fonts that
supports Tamil, e.g. \textsc{tamil letter au} at \uni{0B94} represents a single 
character <ஔ>, composed of two glyphs <ஓ> and <ன>. Perhaps confusingly, 
in the Unicode Standard there are also two individual characters, 
i.e.\ \textsc{tamil letter oo} at \uni{0B93} and 
\uni{0BA9} \textsc{tamil letter nnna}, each of which is a glyph. Another example is 
Sinhala \textsc{sinhala vowel sign kombu deka} at \uni{0DDB} <ෛ>, which is 
visually two glyphs, each represented by \textsc{sinhala vowel sign kombuva} 
at \uni{0DD9} < ෙ>.

>>>>

Second, a single character may be rendered as a sequence of multiple glyphs. For
example, in Tamil one Unicode character may result in a combination of a
consonant and vowel, which are rendered as two adjacent glyphs by fonts that
supports Tamil, e.g. \textsc{tamil letter au} at \uni{0B94} represents a single 
character <\tamil{ஔ}>, composed of two glyphs <\tamil{ஓ}> and <\tamil{ன}>. Perhaps confusingly, 
in the Unicode Standard there are also two individual characters, 
i.e.\ \textsc{tamil letter oo} at \uni{0B93} and 
\uni{0BA9} \textsc{tamil letter nnna}, each of which is a glyph. Another example is 
Sinhala \textsc{sinhala vowel sign kombu deka} at \uni{0DDB} <\sinhala{ෛ}>, which is 
visually two glyphs, each represented by \textsc{sinhala vowel sign kombuva} 
at \uni{0DD9} <\sinhala{ ෙ}>.
